Stochastic Variance Reduced Policy Gradient

### 2018-01-31 svrpg.tex
added comment to main theorem

We can now state the following key result (proof in Appendix \ref{app:proofs}):
\begin{restatable}[Convergence of the SVRPG algorithm]{theorem}{convergence}\label{theo:convergence}
Under Assumptions \ref{ass:bounded_score}, \ref{ass:REINFORCE} and \ref{ass:M2}, the parameter vector $\vtheta_A$ returned by Algorithm \ref{alg:svrpg} after $T=m\times S$ iterations has, for some positive constants $\psi,\zeta, \xi$ and for proper choice of the step size $\alpha$ and the epoch size $m$, the following property:
\begin{align*}
	&\EVV[]
	{\norm[]{\nabla J(\vtheta_A)}^2} 
		\leq
		\frac{J(\vtheta^*)-J(\vtheta_0)}{\psi T} +
		\frac{\zeta}{N}
		+\frac{\xi}{B}
\end{align*}
\end{restatable}
\todomat{Comment theorem}

@@

\section{Experiments}
We have designed our experiments to investigate whether:
\begin{enumerate}
\item The algorithm reaches high value of the reward function faster than GPOMDP.
\item Averagely SVRPG keep the reward function more stable than GPOMDP.
\end{enumerate}

>>>>

We can now state the following key result:
\begin{restatable}[Convergence of the SVRPG algorithm]{theorem}{convergence}\label{theo:convergence}
Under Assumptions \ref{ass:bounded_score}, \ref{ass:REINFORCE} and \ref{ass:M2}, the parameter vector $\vtheta_A$ returned by Algorithm \ref{alg:svrpg} after $T=m\times S$ iterations has, for some positive constants $\psi,\zeta, \xi$ and for proper choice of the step size $\alpha$ and the epoch size $m$, the following property:
\begin{align*}
	&\EVV[]
	{\norm[]{\nabla J(\vtheta_A)}^2} 
		\leq
		\frac{J(\vtheta^*)-J(\vtheta_0)}{\psi T} +
		\frac{\zeta}{N}
		+\frac{\xi}{B}
\end{align*}
\end{restatable}
Specific constants and meta-parameter constraints are provided in the proof of the theorem in Appendix \ref{app:proofs}. In Section \ref{sec:stopping}, instead, we propose a joint selection of step size $\alpha$ and epoch size $m$ which is more suited for applications. 
The $\mathcal{O}(\nicefrac{1}{T})$ term is coherent with results on non-convex SVRG, \eg \cite{reddi2016stochastic}; the $\mathcal{O}(\nicefrac{1}{N})$ term is due to full gradient approximation and is analogous to the one in \cite{harikandeh2015stopwasting}; the $\mathcal{O}(\nicefrac{1}{B})$ term is due to importance weighting. To achieve true convergence, both the batch size $N$ and the mini-batch size $B$ should increase over time. In practice, it is enough to choose $N$ and $B$ large enough to make the second and the third term negligible, \ie to mitigate the variance introduced by full gradient approximation and importance sampling respectively. Since the optimal configuration may be task-dependent, we leave this choice to the empirical analysis of Section \ref{sec:exp}.

@@

\section{Experiments}\label{sec:exp}
We have designed our experiments to investigate whether:
\begin{enumerate}
\item The algorithm reaches high value of the reward function faster than GPOMDP.
\item Averagely SVRPG keep the reward function more stable than GPOMDP.
\end{enumerate}
